\documentclass{beamer}

% Theme selection
\usetheme{Madrid}
\usecolortheme{beaver}

\title{Accessible Learning through Music: A Hackathon Project}
\author{Your Team Name}
\date{\today}

\begin{document}

% Title Slide
\begin{frame}
    \titlepage
\end{frame}

% Introduction
\begin{frame}{Introduction}
    \begin{itemize}
        \item Accessibility tool leveraging music for memory and learning.
        \item Designed for individuals with dyslexia and memory challenges.
        \item Converts text into songs with genre and length customization.
    \end{itemize}
\end{frame}

% Problem Statement
\begin{frame}{The Problem}
    \begin{itemize}
        \item 15-20\% of the population has some form of language-based learning disability (Yale Center for Dyslexia & Creativity).
        \item 80\% of people with learning disabilities struggle with dyslexia.
        \item Traditional learning methods may not be effective for everyone.
        \item Need for engaging, multisensory learning tools.
    \end{itemize}
\end{frame}

% Features Overview
\begin{frame}{Key Features}
    \begin{itemize}
        \item Text-to-song conversion with customizable genre and length.
        \item Shareable songs with accessible lyrics display.
        \item Karaoke mode with dynamic lyric visibility.
        \item VR environments for immersive learning experiences.
        \item Multiplayer VR for collaborative learning and singing.
    \end{itemize}
\end{frame}

% Why Music Helps Learning
\begin{frame}{Why Music Helps Learning}
    \begin{itemize}
        \item Music activates multiple brain areas, including memory-related regions.
        \item Studies show a 40\% increase in recall when information is presented musically (Wallace, 1994).
        \item Encourages repetition in an enjoyable format.
    \end{itemize}
\end{frame}

% Research Supporting the Concept
\begin{frame}{Supporting Research}
    \begin{itemize}
        \item Mayer, R. E. (2009): Multimedia learning enhances comprehension.
        \item Chandrasekaran & Kraus (2010): Music improves speech processing.
        \item Besson, Chobert & Marie (2011): Music enhances attention and memory.
        \item Overy (2003): Musical interventions aid dyslexic learners.
        \item Wallace (1994): Melodies improve text recall by up to 40\%.
        \item Thaut, Peterson & McIntosh (2005): Music-based mnemonics boost brain plasticity and improve memory by 30\%.
    \end{itemize}
\end{frame}

% Feature Deep Dive: Text-to-Song Conversion
\begin{frame}{Feature: Text-to-Song Conversion}
    \begin{itemize}
        \item Users input text and choose genre + length.
        \item AI-generated melody and lyrics enhance memorization.
        \item Studies show musical mnemonics improve recall rates by 35\% (Thaut et al., 2005).
    \end{itemize}
\end{frame}

% Feature Deep Dive: Accessibility Options
\begin{frame}{Feature: Accessibility Options}
    \begin{itemize}
        \item Dyslexia-friendly fonts and color settings improve readability by 20\%.
        \item Karaoke mode for guided recall increases engagement by 50\%.
        \item Visual and audio enhancements for various needs.
    \end{itemize}
\end{frame}

% Feature Deep Dive: VR and Multiplayer
\begin{frame}{Feature: VR and Multiplayer}
    \begin{itemize}
        \item Choose immersive learning environments (concert, ocean, etc.).
        \item Multiplayer mode for collaborative learning improves retention by 25\%.
        \item Enhances engagement through interactivity.
    \end{itemize}
\end{frame}

% Impact on Learning
\begin{frame}{Impact on Learning}
    \begin{itemize}
        \item Improves retention through active engagement (up to 40\% better recall).
        \item Makes learning fun and accessible to all.
        \item Encourages social and collaborative learning, leading to 30\% better knowledge retention.
    \end{itemize}
\end{frame}

% Conclusion
\begin{frame}{Conclusion}
    \begin{itemize}
        \item Innovative tool combining music and learning.
        \item Research-backed approach for accessibility.
        \item Promotes immersive and inclusive education.
        \item Join us in making learning more engaging and effective!
    \end{itemize}
\end{frame}

\end{document}
